### 2013-08-01 Tex/chapters/results.tex
Überblick über die Observablen gegeben
Kleinere Fehlerbereinigungen

        \chi \propto \abs{T-T_{c}}^{-\beta}

@@

    be a power law. But not obligatory e.g.\ the critical "exponent" \(\alpha\)
    corresponding to the divergence of the specific heat \(c\) for the two dimensional
    Ising model diverges logarithmic and is nominally \(\alpha = 0\).
    Because of this, \(\alpha\) will not be considered in this section.\\

@@

        g          &= \frac{3}{2}\brac{1-\frac{\avg{m^4}}{3\avg{m^2}^2}} \propto \tilde{G}\brac{L^\frac{1}{\nu}\brac{T-T_c}}

@@

    Binder cumulant \cite{Binder1981} and \(\tilde{M}, \tilde{C}\) and \(\tilde{G}\)

@@

    shows the collapse for the mean absolute magnetisation per site \(\avg{\abs{m}}\) for \(\sigma=0\),

@@

        \subfigure[Magnetisation $\avg{\abs{m}}$][]

@@

        \subfigure[Finite Size Scaling of the Magnetisation $\avg{\abs{m}}$][]

@@

        \caption{Critical exponents for different $\sigma$}

@@

        \caption{Critical temperatures for different $\sigma$}

>>>>

        \chi \propto \abs{T-T_{c}}^{-\gamma}
        \label{eq:critExp:gamma}
    And the infinite slope of the magnetization can be approximated in
    the direction of lower \(T\) by
        m \propto \abs{T-T_{c}}^{-\beta}

@@

    be a power law, as in the both examples above. But not obligatory e.g.\
    the critical "exponent" \(\alpha\) corresponding to the divergence of
    the specific heat \(c\) diverges logarithmic for the two dimensional
    Ising model and is nominally \(\alpha = 0\).
    For that reason, \(\alpha\) will not be considered in this section.\\

@@

        g         &\propto \tilde{G}\brac{L^\frac{1}{\nu}\brac{T-T_c}}

@@

    Binder cumulant (see eq. \eqref{eq:binder}) and \(\tilde{M}, \tilde{C}\) and \(\tilde{G}\)

@@

    shows the collapse for the mean absolute magnetization per site \(\avg{\abs{m}}\) for \(\sigma=0\),

@@

        \subfigure[Magnetization $\avg{\abs{m}}$][]

@@

        \subfigure[Finite Size Scaling of the Magnetization $\avg{\abs{m}}$][]

@@

        \caption[Critical Exponents for Different $\sigma$]{Critical exponents for different $\sigma$}

@@

        \caption[Critical Temperatures for Different $\sigma$]{Critical temperatures for different $\sigma$}
